Agents and you, a brief summary

### 2015-10-29 agents/summery.tex
finished 2apl notes I think

\subsection{Transitions}
Execution of a belief update action $\alpha$ modifies the belief and goal
bases. $Update$ is an update function that is specified by the believe
update actions and $\gamma'=\gamma - \{\psi \in \gamma | \sigma' \vDash \psi\}$.
Which basically says that $\gamma'$ is equal to $\gamma$ minus the update.

@@

\end{prooftree}
\section{Markov}

>>>>

\subsection{Transitions}
The confiugrations described \emph{what} can change where transition
will describe \emph{how} they can change.

$\vDash$ Describes a first order entailment relation. As I understand
this means $A \vDash B$ there exsits a $B$ in $A$ which has an entailment
to $A$. So $A$ is a set of things and a $B$ like thing exists in $A$.
\subsubsection{Belief update}
Execution of a belief update action $\alpha$ modifies the belief and goal
bases. $Update$ is an update function that is specified by the believe
update actions and $\gamma'=\gamma - \{\psi \in \gamma | \sigma' \vDash \psi\}$.
Which basically says that $\gamma'$ is equal to $\gamma$ minus the update.

@@

\end{prooftree}

So on the left side of the arrow, the plan is to do a believeUpdate $\alpha$
on the right side this is done so its removed from the plans and the believes
\emph{and} goals are modified. The goals are modified to because if a believe
with the same name as a goal becomes true than the goal is removed. (this is
a design decision btw, its just how 2apl works).

\subsubsection{Adopta goal}
Execution of a goal adopt action adopta(g) adds the goal to the beginning of
the goal base. If the goal $g$ trough assignment $\theta$ does not already
exists in goalbase.

\begin{prooftree}
	\AxiomC{$\sigma \nvDash g\theta$}
	\UnaryInfC{$\langle 
		i, \sigma, [\gamma_1, \cdots, y_n], \{(adopta(g),id)\}, \theta, \xi, 
	\rangle \to \langle 
		i, \sigma, [g\theta,\gamma_1, \cdots, y_n], \{\}, \theta, \xi, 
	\rangle$}
\end{prooftree}

So the agent comes accross a adopta method in the plan base $\Pi$, if
the associated believe of the goal is not true then you can start adding
it.

Note that in the slides the environment was also part of this action. But I
think this was a mistake, because in the paper of goaldynamic actions there
isn't a mention of an environment. Besides it doesn't make sense to include
the environment in an agent configuration.

\subsubsection{Applying planning goal rules}
The structure of a PG-rule in 2apl is as follows:

\[\kappa <- \beta | \pi \]

Where $\kappa$ is the name of the plan.
$\beta$ is the condition that is applied before
executing the plan (basically a big if around the plan). $\pi$ is
the body of the plan, a set of instructions.

\begin{prooftree}
	\AxiomC{$\gamma \vDash \kappa \tau_1 \quad \& \quad
	\sigma \vDash \beta \tau_1 \tau_2$}
	\UnaryInfC{$\langle
		i, \sigma, \gamma, \Pi, \theta, \xi
	\rangle \to \langle
	i, \sigma, \gamma, \Pi \cup \{ \pi \tau_1 \tau_2 \}, \theta, \xi
	\rangle$}
\end{prooftree}

The transition can be executed if $\kappa$ is an active goal (this valuation
is stored in $\tau_1$ \emph{and} $\beta$ is true according to the believe 
base (this eveluation is stored in $\tau_2$). If all these things are true
then $\pi$ is added to the plan base $\Pi$ \emph{but} it will only be executed
if $\tau_1$ and $\tau_2$ return true.

\section{Markov}
